---
title: "Assignment 4 - Coordinating Heart Rate"
author: "Riccardo Fusaroli"
date: "November 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Load in data
setwd("~/R/R - Datascripts/Assignment 4/Heart-and-Respiration")
#Load library
library(ggplot2);library(pastecs);library(rmarkdown);library(tidyr);
library(dplyr);library(QuantPsyc);library(VIF);library(stringr);library(tidytext);library(DHARMa)
library(lme4);library(lmerTest);library(psych);library(MuMIn);library(tidyverse);library(magrittr);library(Metrics);library(caret);library(readtext);library(readr)


library(crqa);library(plyr);library(Matrix);library(tseriesChaos);library(deSolve);library(fields);library(spam);library(grid);library(groupdata2)


files = list.files(path = "~/R/R - Datascripts/Assignment 4/Heart-and-Respiration/CleanData",pattern="*.csv")





```


## Analysing Heart Rate and Respiration data

The goal of this assignment is to first familiarize you with heart rate, and respiration data and their preprocessing. The second part explores how to analyze interpersonal coordination of these signals.

These are the questions you need to be able to answer at the end of the assignment (aka that you need to submit as part of the portfolio)

#1) How do you preprocess heart rate and respiration data? Describe the process. If any data needs to be excluded, list the excluded data and motivate the exclusion.

#2) Do you observe interpersonal coordination in heart rate and respiration? Describe your control baseline, the method used to quantify coordination, and the statistical models used to infer whether coordination was higher than in the baseline. Report the results of the models.

#3) Do you observe differences in coordination between conditions? Report the models and results.

#4) Is respiration coordination a likely driver of heart rate coordination? Describe how you would test for it. Bonus points if you actually run the tests and report methods and results.

N.B. to give you a bit more data I included data from last year (Study1) and from your class (Study2). Note that synchronouns and turn-taking are the same across both studies, but the third condition is different: last year it was self-paced joint reading; this year it was the tv-series conversation. So you might want to exclude the self-paced reading (but, up to you!)

## Step by step suggestions to solve the assignment

### Exploring physiological signals

#1) How do you preprocess heart rate and respiration data? Describe the process. If any data needs to be excluded, list the excluded data and motivate the exclusion.
- Choose one pair (one pair, 1 conditions)
- Load the logs
- Produce a plot of the participants' respiration signal and a different one of the participants' HR signal (for inspecting whether the data is usable)
  N.B: remember the slides: artifacts, downsampling, scaling.
  N.B. The gridExtra::grid.arrange() function allows you to display the plots side by side. E.g. grid.arrange(plot1, plot2, plot3, ncol=3)

```{r}

# 
#Make plot of respiration signal, to estimate if data is usable
#Make a recurrence profile.

# Profile=drpdfromts(pair1$Resp1, pair1$Resp2,datatype = 'continuous',ws=50, radius=10)
# str(Profile)
# #Take profile and mulitple by 100 to represent recurrence as a percent
# profile = Profile$profile*100

#To plot the lags properly on the x axis, we have to recsontruct the timecourse of the lags from the ws information.
# timecourse = round( seq(-5000,5000,100)/1000, digit = 1)
# 
# #Take lag at where maximal recurrence is observed
# mxlag = Profile$maxlag
# 
# Prof=data.frame(profile)
#upSample(Prof, pair1)
#downSample(pair1, Prof)
# ggplot(Prof, aes(timecourse,profile))+geom_line() + geom_vline(xintercept = timecourse[mxlag], colour='red')
# paste("maxlag:", timecourse[Profile$mxlag], "sec."),
#        at = timecourse[Profile$mxlag] + 1.2, side = 3, col = "red", line = -1.2, cex = .8)

#We get a larger timecourse, which shows more data, our maxlag is 1.6 sec.
# 
# 
# #Just to see what happens if we zoom in
# #Make plot of respiration signal, to estimate if data is usable
# #Make a recurrence profile.
# 
# #Make plot of respiration signal, to estimate if data is usable
# #Make a recurrence profile.
# 
# Profile=drpdfromts(pair1$Resp1, pair1$Resp2,datatype = 'continuous',ws=100, radius=10)
# str(Profile)
# #Take profile and mulitple by 100 to represent recurrence as a percent
# profile = Profile$profile*100
# 
# #To plot the lags properly on the x axis, we have to recsontruct the timecourse of the lags from the ws information.  
# timecourse = round( seq(-3800,3800,38)/1000, digit = 1)
# 
# #Take lag at where maximal recurrence is observed
# mxlag2 = Profile$maxlag
# 
# Prof2=data.frame(profile)
# #upSample(Prof, pair1)
# #downSample(pair1, Prof)
# ggplot(Prof2, aes(timecourse,profile))+geom_line()+ geom_vline(xintercept = timecourse[mxlag], colour='red') 
# # paste("maxlag:", timecourse[Profile$mxlag], "sec."), 
# #        at = timecourse[Profile$mxlag] + 1.2, side = 3, col = "red", line = -1.2, cex = .8)
# 
# #We get a very different graph, but keep same max lag (1.6 sec.), but we get a more accurate view.
# 
# #

```

```{r}
#Load a random pair, synchronous condition and turn taking
pair5_Sync = read.table("~/R/R - Datascripts/Assignment 4/Heart-and-Respiration/CleanData/Study2_G5_T1_Synchronous.csv", header=T, sep = ",")
pair5_TT = read.table("~/R/R - Datascripts/Assignment 4/Heart-and-Respiration/CleanData/Study2_G5_T2_TurnTaking.csv", header=T, sep = ",")


ggplot(pair5_Sync, aes(time)) + 
  geom_line(aes(y = Resp1, colour = "Resp1")) + 
  geom_line(aes(y = Resp2, colour = "Resp2"))





#Remove outliers!
#Outlier removal function:
removeOuts <- function(ts,threshold){
  ts[ts > (mean(ts, na.rm = TRUE) + 
       (threshold*sd(ts,na.rm = TRUE))) |
  ts <(mean(ts, na.rm = TRUE) -
         (threshold*sd(ts,na.rm = TRUE)))] =
    mean(ts, na.rm = TRUE)
  return(ts)}
threshold = 2.5


#Sync condition___________________________________________________________________________________

#Downsampling! IT MAKES SENSE NOW!!!

#Syn data condition
library(groupdata2)
Sync_data = pair5_Sync %>%
  group(n = 100, method= "greedy") %>%
          dplyr::summarise(
            time = mean(time, na.rm = T),
            Resp1 = mean(Resp1, na.rm = T),
            Resp2 = mean(Resp2, na.rm = T),
            HR1 = mean(HR1, na.rm = T),
            HR2 = mean(HR2, na.rm = T))
#First plot, looks messy
ggplot(Sync_data, aes(time)) + 
  geom_line(aes(y = Resp1, colour = "Resp1")) + 
  geom_line(aes(y = Resp2, colour = "Resp2"))


#Use function
#Sync, remove outliers
threshold = 2.5
Sync_data$Resp1 = removeOuts(Sync_data$Resp1, threshold)
Sync_data$Resp2 = removeOuts(Sync_data$Resp2, threshold)
Sync_data$HR1 = removeOuts(Sync_data$HR1, threshold)
Sync_data$HR2 = removeOuts(Sync_data$HR2, threshold)

#Second plot after removal function - Sync
ggplot(Sync_data, aes(time)) + 
  geom_line(aes(y = Resp1, colour = "Resp1")) + 
  geom_line(aes(y = Resp2, colour = "Resp2"))

ggplot(Sync_data, aes(time)) + 
  geom_line(aes(y = HR1, colour = "HR1")) + 
  geom_line(aes(y = HR2, colour = "HR2"))

#Scale the two respirations to same baseline(ish), so it's easier to compare
#Scaling the signals:
#Sync
Sync_data$Resp1S=scale(Sync_data$Resp1)  
Sync_data$Resp2S=scale(Sync_data$Resp2)  
Sync_data$HR1S=scale(Sync_data$HR1)
Sync_data$HR2S=scale(Sync_data$HR2)

Sync_plot_RP <- ggplot(Sync_data, aes(time)) + 
  geom_line(aes(y = Resp1S, colour = "Resp1")) + 
  geom_line(aes(y = Resp2S, colour = "Resp2")) + 
  geom_hline(yintercept=0, col = "grey") +
  labs(title = "Syncronised Data")
Sync_plot_RP

Sync_plot_HR <-ggplot(Sync_data, aes(time)) + 
  geom_line(aes(y = HR1S, colour = "HR1")) + 
  geom_line(aes(y = HR2S, colour = "HR2")) +
  geom_hline(yintercept=0, col = "grey") +
  labs(title = "Syncronised Data")
Sync_plot_HR

#Turn Taking Condition___________________________________________________________________
#TT

TT_data = pair5_TT %>%
  group(n = 100, method= "greedy") %>%
          dplyr::summarise(
            time = mean(time, na.rm = T),
            Resp1 = mean(Resp1, na.rm = T),
            Resp2 = mean(Resp2, na.rm = T),
            HR1 = mean(HR1, na.rm = T),
            HR2 = mean(HR2, na.rm = T))

#TT Remove outliers
threshold = 2.5
TT_data$Resp1 = removeOuts(TT_data$Resp1, threshold)
TT_data$Resp2 = removeOuts(TT_data$Resp2, threshold)
TT_data$HR1 = removeOuts(TT_data$HR1, threshold)
TT_data$HR2 = removeOuts(TT_data$HR2, threshold)


#TT scale 
TT_data$Resp1S=scale(TT_data$Resp1)  
TT_data$Resp2S=scale(TT_data$Resp2)  
TT_data$HR1S=scale(TT_data$HR1)
TT_data$HR2S=scale(TT_data$HR2)


#TT Finished plots
TT_plot_RP <- ggplot(TT_data, aes(time)) + 
  geom_line(aes(y = Resp1S, colour = "Resp1TT")) + 
  geom_line(aes(y = Resp2S, colour = "Resp2TT")) + 
  geom_hline(yintercept=0, col = "grey") +
  labs(title = "Turn Taking Data")
TT_plot_RP

TT_plot_HR <-ggplot(TT_data, aes(time)) + 
  geom_line(aes(y = HR1S, colour = "HR1TT")) + 
  geom_line(aes(y = HR2S, colour = "HR2TT")) +
  geom_hline(yintercept=0, col = "grey") +
  labs(title = "Turn Taking Data")
TT_plot_HR

#Put plots together
gridExtra::grid.arrange(Sync_plot_RP, Sync_plot_HR, TT_plot_RP, TT_plot_HR)
```
#Can you eye-ball which condition if any displays more physiological coordination?
It seems that there is more coordination in respiration for both conditions. 


- Run crqa on heart rate and respiration data (find parameters, run crqa)
```{r}
#Sync Condition _________________________________________________________________________

#Respiration
#optimize paramters
par = list(lgM =  35, radiusspan = 400, radiussample = 10, normalize = 0, rescale = 1, mindiagline = 2, 
             minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, fnnpercent = 10, typeami = "maxlag")

#Use function
optimizeParam(Sync_data$Resp1S, Sync_data$Resp2S, par, min.rec = 2, max.rec = 5)

#Use results for crqa
Sync_RP_CRQA <- try(crqa(Sync_data$Resp1S, Sync_data$Resp2S, embed = 19, delay = 33, radius = 66.77911, normalize = 0, rescale = 2, mindiagline = 2, minvertline = 2))

Sync_RP_CRQA

#Plot crqa
# Sync_RP1=Sync_RP1_CRQA$RP
# Sync_RP1_plot = matrix(as.numeric(Sync_RP1), nrow = ncol(Sync_RP1)) 
# cols = c("white","blue4")
# image(Sync_RP1_plot, xlab = "Resp1 Sync", ylab = "Resp2 Sync", col = cols)
# Sync_RP1_plot

#Heartrate
#optimize paramters
optimizeParam(Sync_data$HR1S, Sync_data$HR2S, par, min.rec = 2, max.rec = 5)

#Use results for crqa
HR_Sync_CRQA <- try(crqa(Sync_data$HR1S,Sync_data$HR2S, embed = 11, delay = 34, radius = 22, normalize = 0, rescale = 2, mindiagline = 2, minvertline = 2))
HR_Sync_CRQA


  
  #Plot crqa
HR_Sync=HR_Sync_CRQA$RP
Sync_HR_plot = matrix(as.numeric(HR_Sync), nrow = ncol(HR_Sync))
cols = c("white","blue4")
image(Sync_HR_plot, xlab = "HR1 Sync", ylab = "HR2 Sync", col = cols)
grobs = list(Sync_HR_plot, HR_Sync)
Sync_HR_plot
# 



#Turn Taking Condition ___________________________________________________________________

#Respiration

#optimize paramters
par = list(lgM =  35, radiusspan = 400, radiussample = 10, normalize = 0, rescale = 1, mindiagline = 2, 
             minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, fnnpercent = 10, typeami = "maxlag")

optimizeParam(TT_data$Resp1S, TT_data$Resp2S, par, min.rec = 2, max.rec = 5)

#Use results for crqa
ResultsR_TT <- try(crqa(TT_data$Resp1S, TT_data$Resp2S, embed = 2, delay = 26, radius = 16.36994, normalize = 0, rescale = 2, mindiagline = 2, minvertline = 2))
ResultsR_TT

# Plot crqa
# RP_TT=ResultsR_TT$RP
# RP_TT = matrix(as.numeric(RP_TT), nrow = ncol(RP_TT)) 
# cols = c("white","blue4")
# image(RP_TT, xlab = "", ylab = "", col = cols)


#Heartrate

#optimize paramters
par = list(lgM =  35, radiusspan = 400, radiussample = 10, normalize = 0, rescale = 1, mindiagline = 2, 
             minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, fnnpercent = 10, typeami = "maxlag")


optimizeParam(TT_data$HR1S, TT_data$HR2S, par, min.rec = 2, max.rec = 5)


#Use results for crqa
ResultsHR_TT <- try(crqa(TT_data$HR1S,TT_data$HR2S, embed = 16, delay = 35, radius = 55.14556, normalize = 0, rescale = 2, mindiagline = 2, minvertline = 2))
ResultsHR_TT

#Plot crqa
# RPHR_TT=ResultsHR_TT$RP
# RPHR_TT = matrix(as.numeric(RPHR_TT), nrow = ncol(RPHR_TT)) 
# cols = c("white","blue4")
# image(RPHR_TT, xlab = "HR1TT", ylab = "HR2TT", col = cols)
# 
# RPHR_TT


```

#Does this tell you more than just eyeballing the plots?



### Systematically pre-process the data
- Loop through all the files (either with a loop or with a function), check which files should be excluded, if any, and save the pre-processed time-series. Tip: plot and visually inspect the data to figure out which should be excluded.
- Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries. Tip: it will often fail, just take whatever parameters you get, select optimal across timeseries parameters and run crqa on all timeseries with those. Tip: double check the rr. When I ran the loop, I got very low rr, so I adjusted the radius until the average of rr across all pairs was approx. 4%.
```{r}

#Outlier removal function:
removeOuts <- function(ts,threshold){
  ts[ts > (mean(ts, na.rm = TRUE) + 
       (threshold*sd(ts,na.rm = TRUE))) |
  ts <(mean(ts, na.rm = TRUE) -
         (threshold*sd(ts,na.rm = TRUE)))] =
    mean(ts, na.rm = TRUE)
  return(ts)}
threshold = 2.5



# files = list.files(path = "C:/Users/emily/OneDrive/Dokumenter/R/R - Datascripts/Assignment 4/Heart-and-Respiration/CleanData",pattern=".csv")

setwd("~/R/R - Datascripts/Assignment 4/Heart-and-Respiration")

preprocFunc = function(file){
  print(file)
  dataName = paste("CleanData/", file, sep = "")
  data = read.csv(dataName)
  
  #Downsample
  data = data %>%
  group(n = 100, method = "greedy") %>%
  dplyr::summarise(
    time = mean(time, na.rm = T),
    HR1 = mean(HR1, na.rm = T),
    HR2 = mean(HR2, na.rm = T),
    Resp1 = mean(Resp1, na.rm = T),
    Resp2 = mean(Resp2, na.rm = T))
  
  #Scale and remove outs
  data$HR1 = scale(removeOuts(data$HR1, threshold))
  data$HR2 = scale(removeOuts(data$HR2, threshold))
  data$Resp1 = scale(removeOuts(data$Resp1, threshold))
  data$Resp2 = scale(removeOuts(data$Resp2, threshold))
  
  
  fileName = paste("dataProc/", file, sep = "")
  
  #Save as new files
  write.csv(data, file = fileName)
}


lapply(files, preprocFunc)




```


```{r}
setwd("~/R/R - Datascripts/Assignment 4/Heart-and-Respiration")

filesProcs = list.files(path = "~/R/R - Datascripts/Assignment 4/Heart-and-Respiration/dataProc",pattern="*.csv")
print(filesProcs)


filesProcs
N = 1

for (file in filesProcs){
  dataName = paste("dataProc/", file, sep = "")
  
  
  data = read.csv(dataName)
  
  #HR
  plotHR = ggplot(data = data) +
  geom_line(aes(x = time, y = HR1), colour = "Red") + 
  geom_line(aes(x = time, y = HR2), colour = "Blue") +
  geom_hline(yintercept=0, col = "grey") +
  labs(x = "time", y = "Heart Rate", title = "Heart Rate")
  
  assign(paste("plotHR", N, sep = ""), plotHR)
  
 
  
  #Resp
  plotResp = ggplot(data = data)+
  geom_line(aes(x = time, y = Resp1), colour = "Red") + 
  geom_line(aes(x = time, y = Resp2), colour = "Blue") +
  geom_hline(yintercept=0, col = "grey") +
  labs(x = "time", y = "Respiration", title = "Respiration")
  
  
  assign(paste("plotResp", N, sep = ""), plotResp)
  
  N = N+1
}

gridExtra::grid.arrange(plotResp1, plotHR1) #Flat resp
gridExtra::grid.arrange(plotResp2, plotHR2) #Flat resp
gridExtra::grid.arrange(plotResp3, plotHR3) #Ok
gridExtra::grid.arrange(plotResp4, plotHR4) #Flat resp
gridExtra::grid.arrange(plotResp5, plotHR5) #Flat resp
gridExtra::grid.arrange(plotResp6, plotHR6) #OK
gridExtra::grid.arrange(plotResp7, plotHR7) #OK 
gridExtra::grid.arrange(plotResp8, plotHR8) #OK
gridExtra::grid.arrange(plotResp9, plotHR9) #Flat HR
gridExtra::grid.arrange(plotResp10, plotHR10) #OK
gridExtra::grid.arrange(plotResp11, plotHR11) #OK
gridExtra::grid.arrange(plotResp12, plotHR12) #OK
gridExtra::grid.arrange(plotResp13, plotHR13) #OK
gridExtra::grid.arrange(plotResp14, plotHR14) #OK
gridExtra::grid.arrange(plotResp15, plotHR15) #OK
gridExtra::grid.arrange(plotResp16, plotHR16) #OK
gridExtra::grid.arrange(plotResp17, plotHR17) #OK
gridExtra::grid.arrange(plotResp18, plotHR18) #OK
gridExtra::grid.arrange(plotResp19, plotHR19) #OK
gridExtra::grid.arrange(plotResp20, plotHR20) #OK
gridExtra::grid.arrange(plotResp21, plotHR21) #OK
gridExtra::grid.arrange(plotResp22, plotHR22) #OK
gridExtra::grid.arrange(plotResp23, plotHR23) #OK
gridExtra::grid.arrange(plotResp24, plotHR24) #OK
gridExtra::grid.arrange(plotResp25, plotHR25) #OK
gridExtra::grid.arrange(plotResp26, plotHR26) #OK
gridExtra::grid.arrange(plotResp27, plotHR27) #OK
gridExtra::grid.arrange(plotResp28, plotHR28) #OK
gridExtra::grid.arrange(plotResp29, plotHR29) #OK
gridExtra::grid.arrange(plotResp30, plotHR30) #OK


filesAnalysis = filesProcs[-c(1,2,4,5,9)]

```

# Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries
```{r}

#setwd("~/R/R - Datascripts/Assignment 4/Heart-and-Respiration")

#Optimize for delay, embed and radius
group = NULL
condition = NULL
trial = NULL
study = NULL

Respdelay = NULL
Respradius = NULL
Respembed = NULL

HRdelay = NULL
HRradius = NULL
HRembed = NULL




n = 1




#Extract optimal parameters
for (file in filesAnalysis){
  #print(file)
  nameFile = paste("dataProc/", file, sep = "")
  #read data
  data = read.csv(nameFile)
  
   #optimizeparam functions
  par = list(lgM = 50, steps = seq(1, 6, 1), radiusspan = 100, radiussample = 40, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2, tw = 0, whiteline = F, recpt = FALSE, fnnpercent = 10, typeami = "mindip")
  
  RespOP = try(optimizeParam(data$Resp1, data$Resp2, par, min.rec = 1, max.rec = 15))
  print(RespOP)
  
  #if statement: If having problem with optimizeparam, it will append NA
  if (length(RespOP) > 1){
    Respradius[n] = RespOP[1]
    Respembed[n] = RespOP[2]
    Respdelay[n] = RespOP[3]
  }
  
  else {
    Respradius[n] = NA
    Respembed[n] = NA
    Respdelay[n] = NA
    
  }
  
  HROp = try(optimizeParam(data$HR1, data$HR2, par, min.rec = 1, max.rec = 15))
  
  print(HROp)
  
  #if statement: If having problem with optimizeparam, it will append NA
  if (length(HROp) > 1){
    HRradius[n] = HROp[1]
    HRembed[n] = HROp[2]
    HRdelay[n] = HROp[3]
  }
  
  else {
    HRradius[n] = NA
    HRembed[n] = NA
    HRdelay[n] = NA
    
  }
  
   #get participant number information
  #would like to extract seperate participant, trial and diagnosis info
  study[n] = substring(file, 6, 6)
  group[n] = substring(sub("_T.*", "", file),9)
  trial[n] = sub(".T*", "", sub("\\_.*", "", sub("^[^T]*", "", file)))
  condition[n] = unlist(strsplit(gsub('.{4}$', '', file), "_"))[4]
  
  
  n = n+ 1
}




#Unlist
Respdelay = unlist(Respdelay)
Respembed = unlist(Respembed)
Respradius = unlist(Respradius)

HRdelay = unlist(HRdelay)
HRembed = unlist(HRembed)
HRradius = unlist(HRradius)

dfOptim = data.frame(study, group, trial, condition, Respembed, Respdelay, Respradius, HRembed, HRdelay, HRradius)



```




```{r}
#Run CRQA analysis with median paramters.

setwd("~/R/R - Datascripts/Assignment 4/Heart-and-Respiration")

 
RespRadiusOptimal = median(dfOptim$Respradius, na.rm = T)
RespEmbedOptimal = median(dfOptim$Respembed, na.rm = T)
RespDelayOptimal = median(dfOptim$Respdelay, na.rm = T)


HRradiusOptimal = median(dfOptim$HRradius, na.rm = T) 
HRembedOptimal = median(dfOptim$HRembed, na.rm = T)
HRdelayOptimal = median(dfOptim$HRdelay, na.rm = T)


#crqaextract

Resp_RR = NULL
Resp_DET = NULL
Resp_NRLINE = NULL
Resp_maxL = NULL
Resp_L = NULL
Resp_ENTR = NULL
Resp_LAM = NULL
Resp_TT = NULL

HR_RR = NULL
HR_DET = NULL
HR_NRLINE = NULL
HR_maxL = NULL
HR_L = NULL
HR_ENTR = NULL
HR_LAM = NULL
HR_TT = NULL


N = 1


for (file in filesAnalysis){

  
  nameFile = paste("dataProc/", file, sep = "")
  #read data
  data = read.csv(nameFile)
  
  #Make CRQA
  HRcrqa = try(crqa(data$HR1, data$HR2, delay = HRdelayOptimal, embed = HRembedOptimal, radius = HRradiusOptimal, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2))
    
  if (length(HRcrqa) > 1){
    HR_RR[N] = HRcrqa[1]
    HR_DET[N] = HRcrqa[2]
    HR_NRLINE[N] = HRcrqa[3]
    HR_maxL[N] = HRcrqa[4]
    HR_L[N] = HRcrqa[5]
    HR_ENTR[N] = HRcrqa[6]
    HR_LAM[N] = HRcrqa[8]
    HR_TT[N] = HRcrqa[9]
    
   }
   else{
    HR_RR[N] = NA
    HR_DET[N] = NA
    HR_NRLINE[N] = NA
    HR_maxL[N] = NA
    HR_L[N] = NA
    HR_ENTR[N] = NA
    HR_LAM[N] = NA
    HR_TT[N] = NA
   }
  #  N = N+1
  # Print(N)
   #Make CRQA
   Respcrqa = try(crqa(data$Resp1, data$Resp2, delay = RespDelayOptimal, embed = RespEmbedOptimal, radius = RespRadiusOptimal, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2))

   if (length(Respcrqa) > 2){
     #Write to lists
     Resp_RR[N] = Respcrqa[1]
     Resp_DET[N] = Respcrqa[2]
     Resp_NRLINE[N] = Respcrqa[3]
     Resp_maxL[N] = Respcrqa[4]
     Resp_L[N] = Respcrqa[5]
     Resp_ENTR[N] = Respcrqa[6]
     Resp_LAM[N] = Respcrqa[8]
     Resp_TT[N] = Respcrqa[9]

   }
   else{
     Resp_RR[N] = NA
     Resp_DET[N] = NA
     Resp_NRLINE[N] = NA
     Resp_maxL[N] = NA
     Resp_L[N] = NA
     Resp_ENTR[N] = NA
     Resp_LAM[N] = NA
     Resp_TT[N] = NA



   }



   N = N+1
   print(N)  


}

#Unlist variables
Resp_RR = unlist(Resp_RR)
Resp_DET = unlist(Resp_DET)
Resp_NRLINE = unlist(Resp_NRLINE)
Resp_maxL = unlist(Resp_maxL)
Resp_L = unlist(Resp_L)
Resp_ENTR = unlist(Resp_ENTR)
Resp_LAM = unlist(Resp_LAM)
Resp_TT = unlist(Resp_TT)

HR_RR = unlist(HR_RR)
HR_DET = unlist(HR_DET)
HR_NRLINE = unlist(HR_NRLINE)
HR_maxL = unlist(HR_maxL)
HR_L = unlist(HR_L)
HR_ENTR = unlist(HR_ENTR)
HR_LAM = unlist(HR_LAM)
HR_TT = unlist(HR_TT)


dfRQA = data.frame(dfOptim,HR_RR, HR_DET, HR_NRLINE, HR_maxL, HR_L, HR_ENTR, HR_LAM, HR_TT, Resp_RR, Resp_DET, Resp_NRLINE, Resp_maxL, Resp_L, Resp_ENTR, Resp_LAM, Resp_TT)

dfRQA = mutate(dfRQA, pair = "Real")

write.csv(dfRQA, file = "CRQAReal.csv", row.names = F )


```




### Creating controls: shuffled controls
 - loop through all pairs and conditions
 - shuffle the timeseries (take a timeseries and rearrange its values in a random order). Tip check the sample() function
 - run crqa and save the output. NB. which delay, embed, radius parameters should you use?
 - statistically compare the crqa indexes in real and shuffled pairs

```{r}

#We shuffilin..shuffilin
library(tidyverse)
#Add column to our already excisting dataframe telling that it is real pairs
dfRQA = mutate(dfRQA, pair = "Real")


#Parameters we want to save
#HR
HR_RR = NULL
HR_DET = NULL
HR_NRLINE = NULL
HR_maxL = NULL
HR_L = NULL
HR_ENTR = NULL
HR_LAM = NULL
HR_TT = NULL
#Resp
resp_RR = NULL
resp_DET = NULL
resp_NRLINE = NULL
resp_maxL = NULL
resp_L = NULL
resp_ENTR = NULL
resp_LAM = NULL
resp_TT = NULL

#N
N = 1



for (file in filesAnalysis){
  nameFile = paste("dataProc/", file, sep = "")
  #read data
  data = read.csv(nameFile)
  
  #Shuffle the data by using sample()
  data = data[sample(data$.groups),]
  
    HRcrqa = try(crqa(data$HR1, data$HR2, delay = 22, embed = 11, radius = 1.993034, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2))
    
  if (length(HRcrqa) > 1){
    HR_RR[N] = HRcrqa[1]
    HR_DET[N] = HRcrqa[2]
    HR_NRLINE[N] = HRcrqa[3]
    HR_maxL[N] = HRcrqa[4]
    HR_L[N] = HRcrqa[5]
    HR_ENTR[N] = HRcrqa[6]
    HR_LAM[N] = HRcrqa[8]
    HR_TT[N] = HRcrqa[9]
    
   }
   else{
    HR_RR[N] = NA
    HR_DET[N] = NA
    HR_NRLINE[N] = NA
    HR_maxL[N] = NA
    HR_L[N] = NA
    HR_ENTR[N] = NA
    HR_LAM[N] = NA
    HR_TT[N] = NA
   }
  #  N = N+1
  # Print(N)
   #Make CRQA
   Respcrqa = try(crqa(data$Resp1, data$Resp2, delay = RespDelayOptimal, embed = RespEmbedOptimal, radius = RespRadiusOptimal, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2))

   if (length(Respcrqa) > 2){
     #Write to lists
     Resp_RR[N] = Respcrqa[1]
     Resp_DET[N] = Respcrqa[2]
     Resp_NRLINE[N] = Respcrqa[3]
     Resp_maxL[N] = Respcrqa[4]
     Resp_L[N] = Respcrqa[5]
     Resp_ENTR[N] = Respcrqa[6]
     Resp_LAM[N] = Respcrqa[8]
     Resp_TT[N] = Respcrqa[9]

   }
   else{
     Resp_RR[N] = NA
     Resp_DET[N] = NA
     Resp_NRLINE[N] = NA
     Resp_maxL[N] = NA
     Resp_L[N] = NA
     Resp_ENTR[N] = NA
     Resp_LAM[N] = NA
     Resp_TT[N] = NA



  }
  
  
  print(N)
  N = N+1
}

#UNLIST

Resp_RR = unlist(Resp_RR)
Resp_DET = unlist(Resp_DET)
Resp_NRLINE = unlist(Resp_NRLINE)
Resp_maxL = unlist(Resp_maxL)
Resp_L = unlist(Resp_L)
Resp_ENTR = unlist(Resp_ENTR)
Resp_LAM = unlist(Resp_LAM)
Resp_TT = unlist(Resp_TT)

HR_RR = unlist(HR_RR)
HR_DET = unlist(HR_DET)
HR_NRLINE = unlist(HR_NRLINE)
HR_maxL = unlist(HR_maxL)
HR_L = unlist(HR_L)
HR_ENTR = unlist(HR_ENTR)
HR_LAM = unlist(HR_LAM)
HR_TT = unlist(HR_TT)


dfRQAShuffle = data.frame(dfOptim,HR_RR, HR_DET, HR_NRLINE, HR_maxL, HR_L, HR_ENTR, HR_LAM, HR_TT, Resp_RR, Resp_DET, Resp_NRLINE, Resp_maxL, Resp_L, Resp_ENTR, Resp_LAM, Resp_TT)


#Insert NAs in delay, embed and radius as we do not calculate new values
dfRQAShuffle = mutate(dfRQAShuffle, pair = "Shuffle")
# dfCRQAShuffle = mutate(dfCRQAShuffle, "HREmbed" = NA, "HRDelay" = NA, "HRRadius" = NA, "respDelay" = NA, "respEmbed" = NA, "respRadius" = NA)

#bind df together
allCRQA = rbind(dfRQA, dfRQAShuffle)
#Save this, eeeeh!!
write.csv(allCRQA, file = "CRQARealShuff.csv", row.names = F)

```

```{r}
#statistically compare the crqa indexes in real and shuffled pairs

#Heart rate
HR_RealShuf_RR <- lm(HR_RR ~ pair, allCRQA)
summary(HR_RealShuf_RR)

HR_RealShuf_DET <- lm(HR_DET ~ pair, allCRQA)
summary(HR_RealShuf_DET)

HR_RealShuf_NRLINE <- lm(HR_NRLINE ~ pair, allCRQA)
summary(HR_RealShuf_NRLINE)

HR_RealShuf_maxL <- lm(HR_maxL ~ pair, allCRQA)
summary(HR_RealShuf_maxL)

HR_RealShuf_L <- lm(HR_L ~ pair, allCRQA)
summary(HR_RealShuf_L)

HR_RealShuf_ENTR <- lm(HR_ENTR ~ pair, allCRQA)
summary(HR_RealShuf_ENTR)

HR_RealShuf_LAM <- lm(HR_LAM ~ pair, allCRQA)
summary(HR_RealShuf_LAM)

HR_RealShuf_TT <- lm(HR_TT ~ pair, allCRQA)
summary(HR_RealShuf_TT)

lm_HRTINGY1<- sjt.lm(HR_RealShuf_RR, HR_RealShuf_DET, HR_RealShuf_NRLINE,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)



lm_HRTINGY2<- sjt.lm(HR_RealShuf_maxL, HR_RealShuf_L, HR_RealShuf_ENTR,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)



lm_HRTINGY3<- sjt.lm(HR_RealShuf_LAM, HR_RealShuf_TT,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)



Resp_RealShuf_RR <- lm(Resp_RR ~ pair, allCRQA)
summary(Resp_RealShuf_RR)

Resp_RealShuf_DET <- lm(Resp_DET ~ pair, allCRQA)
summary(Resp_RealShuf_DET)

Resp_RealShuf_NRLINE <- lm(Resp_NRLINE ~ pair, allCRQA)
summary(Resp_RealShuf_NRLINE)

Resp_RealShuf_maxL <- lm(Resp_maxL ~ pair, allCRQA)
summary(Resp_RealShuf_maxL)

Resp_RealShuf_L <- lm(Resp_L ~ pair, allCRQA)
summary(Resp_RealShuf_L)

Resp_RealShuf_ENTR <- lm(Resp_ENTR ~ pair, allCRQA)
summary(Resp_RealShuf_ENTR)

Resp_RealShuf_LAM <- lm(Resp_LAM ~ pair, allCRQA)
summary(Resp_RealShuf_LAM)

Resp_RealShuf_TT <- lm(Resp_TT ~ pair, allCRQA)
summary(Resp_RealShuf_TT)


lm_RESPTINGY1<- sjt.lm(Resp_RealShuf_RR, Resp_RealShuf_DET, Resp_RealShuf_NRLINE,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)



lm_RESPTINGY2<- sjt.lm(Resp_RealShuf_maxL,Resp_RealShuf_L, Resp_RealShuf_ENTR,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)


lm_RESPTINGY3<- sjt.lm(Resp_RealShuf_LAM, Resp_RealShuf_TT,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)







```
 
 
### TRICKY! Creating controls: surrogate pair controls
 - Per each real pair, identify at least one surrogate pair (matching one of the participants, with somebody doing the same task, but in a different pair). Tip: Celine will share a commented script
 - Run crqa on all the surrogate pairs and save the output. NB. which delay, embed, radius parameters should you use?
 - Test whether crqa shows a difference between real and surrogate pairs

#Study1
```{r}
#Celines code. Changed a little thanks to Peter and Karl
#Making surrogates

setwd("~/R/R - Datascripts/Assignment 4/Heart-and-Respiration/")
prepro_filelist = list.files(path= "~/R/R - Datascripts/Assignment 4/Heart-and-Respiration/dataProc", pattern = "Study1") # load the preprocessed files


num=str_extract_all(prepro_filelist, "\\d+") #extract all numbers in the file name (i.e Study?_G?_T?)

df= as.data.frame(t(as.data.frame(num))) #create a transposed (i.e. "tipped") dataframe of these number
rownames(df)<-NULL #Remove rownames.

pairs=as.numeric(unique(as.numeric(as.character(df$V2)))) #create pairs, i.e. unique group numbers

SurrogateList <- expand.grid(a = pairs, b = pairs) # expand.grid combines all possible combinations of a given vector
SurrogateList = subset(SurrogateList, a != b) # Ensure that pair 1 (i.e group1) doesn't get paired with it self.

# Per each condition
for (co in c("Synchronous","TurnTaking","SelfPaced")){ #loop through a list of condintions 
  for (i in 1:nrow(SurrogateList)){ #and loop through all the pairings of the surrogate list

  #start recreate filenames from the working directory based on the matching from the surrogatelist
  f1=paste0('Study1_G',SurrogateList$a[i]) #Insert group numeber from Surrogatelist 
  f2=paste0('Study1_G',SurrogateList$b[i])
  
  file1=prepro_filelist[grepl(f1,prepro_filelist) & grepl(co,prepro_filelist)] #insert conditions as well.
  file2=prepro_filelist[grepl(f2,prepro_filelist) & grepl(co,prepro_filelist)]
  
  d1=read.csv(file1) #Load the recreated filenames
  
  d2=read.csv(file2) 
  
  #Ensure both dataframes have the same length
  if (nrow(d1)>nrow(d2)){
    d1=d1[1:nrow(d2),]
  } else {
    d2=d2[1:nrow(d1),]
  }
  
  #creation of surrogate files. (Riccardo's idea of having fun and completely overdoing it ;-) ) 
  #per each 2 pairs there are 4 possible surrogate pairs: 
  #pair1person1 w pair2person2; 
  d3=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp2,HR1=d1$HR1,HR2=d2$HR2,Resp1S=d1$Resp1,Resp2S=d2$Resp2,HR1S=d1$HR1,HR2S=d2$HR2)
  #pair1person2 w pair2person2;
  d4=data.frame(Resp1=d2$Resp1,Resp2=d1$Resp2,HR1=d2$HR1,HR2=d1$HR2,Resp1S=d2$Resp1,Resp2S=d1$Resp2,HR1S=d2$HR1,HR2S=d1$HR2)
  
  #pair1person1 w pair2person1;
  d5=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp1,HR1=d1$HR1,HR2=d2$HR1,Resp1S=d1$Resp1,Resp2S=d2$Resp1,HR1S=d1$HR1,HR2S=d2$HR1)
  #pair1person2 w pair2person2
  d6=data.frame(Resp1=d2$Resp2,Resp2=d1$Resp2,HR1=d2$HR2,HR2=d1$HR2,Resp1S=d2$Resp2,Resp2S=d1$Resp2,HR1S=d2$HR2,HR2S=d1$HR2)
  
  #Make filenames that tells which pairs have been mixed
  file3=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"a_",co,".csv")
  file4=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"b_",co,".csv")
  file5=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"c_",co,".csv")
  file6=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"d_",co,".csv")
  
  #write csv files
  write_csv(d3,file.path("surrogate",file3))
  write_csv(d4,file.path("surrogate",file4))
  write_csv(d5,file.path("surrogate",file5))
  write_csv(d6,file.path("surrogate",file6))
  }
}

##NOW DO THE SAME FOR STUDY 2##
```


#Study 2
```{r}

setwd("~/R/R - Datascripts/Assignment 4/Heart-and-Respiration/")
prepro_filelist = list.files(path= "~/R/R - Datascripts/Assignment 4/Heart-and-Respiration/dataProc", pattern = "Study2") # load the preprocessed files


num=str_extract_all(prepro_filelist, "\\d+") #extract all numbers in the file name (i.e Study?_G?_T?)

df= as.data.frame(t(as.data.frame(num))) #create a transposed (i.e. "tipped") dataframe of these number
rownames(df)<-NULL #Remove rownames.

pairs=as.numeric(unique(as.numeric(as.character(df$V2)))) #create pairs, i.e. unique group numbers

SurrogateList <- expand.grid(a = pairs, b = pairs) # expand.grid combines all possible combinations of a given vector
SurrogateList = subset(SurrogateList, a != b) # Ensure that pair 1 (i.e group1) doesn't get paired with it self.

# Per each condition
for (co in c("Synchronous","TurnTaking","SelfPaced")){ #loop through a list of condintions 
  for (i in 1:nrow(SurrogateList)){ #and loop through all the pairings of the surrogate list

  #start recreate filenames from the working directory based on the matching from the surrogatelist
  f1=paste0('Study2_G',SurrogateList$a[i]) #Insert group numeber from Surrogatelist 
  f2=paste0('Study2_G',SurrogateList$b[i])
  
  file1=prepro_filelist[grepl(f1,prepro_filelist) & grepl(co,prepro_filelist)] #insert conditions as well.
  file2=prepro_filelist[grepl(f2,prepro_filelist) & grepl(co,prepro_filelist)]
  
  d1=read.csv(file1) #Load the recreated filenames
  
  d2=read.csv(file2) 
  
  #Ensure both dataframes have the same length
  if (nrow(d1)>nrow(d2)){
    d1=d1[1:nrow(d2),]
  } else {
    d2=d2[1:nrow(d1),]
  }
  
  #creation of surrogate files. (Riccardo's idea of having fun and completely overdoing it ;-) ) 
  #per each 2 pairs there are 4 possible surrogate pairs: 
  #pair1person1 w pair2person2; 
  d3=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp2,HR1=d1$HR1,HR2=d2$HR2,Resp1S=d1$Resp1,Resp2S=d2$Resp2,HR1S=d1$HR1,HR2S=d2$HR2)
  #pair1person2 w pair2person2;
  d4=data.frame(Resp1=d2$Resp1,Resp2=d1$Resp2,HR1=d2$HR1,HR2=d1$HR2,Resp1S=d2$Resp1,Resp2S=d1$Resp2,HR1S=d2$HR1,HR2S=d1$HR2)
  
  #pair1person1 w pair2person1;
  d5=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp1,HR1=d1$HR1,HR2=d2$HR1,Resp1S=d1$Resp1,Resp2S=d2$Resp1,HR1S=d1$HR1,HR2S=d2$HR1)
  #pair1person2 w pair2person2
  d6=data.frame(Resp1=d2$Resp2,Resp2=d1$Resp2,HR1=d2$HR2,HR2=d1$HR2,Resp1S=d2$Resp2,Resp2S=d1$Resp2,HR1S=d2$HR2,HR2S=d1$HR2)
  
  #Make filenames that tells which pairs have been mixed
  file3=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"a_",co,".csv")
  file4=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"b_",co,".csv")
  file5=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"c_",co,".csv")
  file6=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"d_",co,".csv")
  
  #write csv files
  write_csv(d3,file.path("surrogate",file3))
  write_csv(d4,file.path("surrogate",file4))
  write_csv(d5,file.path("surrogate",file5))
  write_csv(d6,file.path("surrogate",file6))
  }
}

```


- Run crqa on all the surrogate pairs and save the output. NB. which delay, embed, radius parameters should you use?
#I use the same parameters as i did for my other two datasets. They have to be done on the same paramters for being comparable.

```{r}
#Load a file list


filesSurgat = list.files(path = "~/R/R - Datascripts/Assignment 4/Heart-and-Respiration/surrogate",pattern="*.csv")
#print(head(filesSurgat))
#Parameters we want to save
#Describ
study = NULL
group = NULL
trial = NULL
condition = NULL
#HR
HR_RR = NULL
HR_DET = NULL
HR_NRLINE = NULL
HR_maxL = NULL
HR_L = NULL
HR_ENTR = NULL
HR_LAM = NULL
HR_TT = NULL
#Resp
Resp_RR = NULL
Resp_DET = NULL
Resp_NRLINE = NULL
Resp_maxL = NULL
Resp_L = NULL
Resp_ENTR = NULL
Resp_LAM = NULL
Resp_TT = NULL

#N
N = 1



for (file in filesSurgat){
  nameFile = paste("surrogate/", file, sep = "")
  #read data
  data = read.csv(nameFile)
  
  
  HRcrqa = try(crqa(data$HR1, data$HR2, delay = HRdelayOptimal, embed = HRembedOptimal, radius = HRradiusOptimal, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2))
    
  if (length(HRcrqa) > 1){
    HR_RR[N] = HRcrqa[1]
    HR_DET[N] = HRcrqa[2]
    HR_NRLINE[N] = HRcrqa[3]
    HR_maxL[N] = HRcrqa[4]
    HR_L[N] = HRcrqa[5]
    HR_ENTR[N] = HRcrqa[6]
    HR_LAM[N] = HRcrqa[8]
    HR_TT[N] = HRcrqa[9]
    
   }
   else{
    HR_RR[N] = NA
    HR_DET[N] = NA
    HR_NRLINE[N] = NA
    HR_maxL[N] = NA
    HR_L[N] = NA
    HR_ENTR[N] = NA
    HR_LAM[N] = NA
    HR_TT[N] = NA
   }
  #  N = N+1
  # Print(N)
   #Make CRQA
  
     
  
   Respcrqa = try(crqa(data$Resp1, data$Resp2, delay = RespDelayOptimal, embed = RespEmbedOptimal, radius = RespRadiusOptimal, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2))

   if (length(Respcrqa) > 2){
     #Write to lists
     Resp_RR[N] = Respcrqa[1]
     Resp_DET[N] = Respcrqa[2]
     Resp_NRLINE[N] = Respcrqa[3]
     Resp_maxL[N] = Respcrqa[4]
     Resp_L[N] = Respcrqa[5]
     Resp_ENTR[N] = Respcrqa[6]
     Resp_LAM[N] = Respcrqa[8]
     Resp_TT[N] = Respcrqa[9]

   }
   else{
     Resp_RR[N] = NA
     Resp_DET[N] = NA
     Resp_NRLINE[N] = NA
     Resp_maxL[N] = NA
     Resp_L[N] = NA
     Resp_ENTR[N] = NA
     Resp_LAM[N] = NA
     Resp_TT[N] = NA



  }
  study[N] = substring(file, 6, 6)
  group[N] = substring(sub("_T.*", "", file),9)
  trial[N] = sub(".T*", "", sub("\\_.*", "", sub("^[^T]*", "", file)))
  condition[N] = unlist(strsplit(gsub('.{4}$', '', file), "_"))[4]
  
  
  
  print(N)
  N = N+1
}

#UNLIST

Resp_RR = unlist(Resp_RR)
Resp_DET = unlist(Resp_DET)
Resp_NRLINE = unlist(Resp_NRLINE)
Resp_maxL = unlist(Resp_maxL)
Resp_L = unlist(Resp_L)
Resp_ENTR = unlist(Resp_ENTR)
Resp_LAM = unlist(Resp_LAM)
Resp_TT = unlist(Resp_TT)

HR_RR = unlist(HR_RR)
HR_DET = unlist(HR_DET)
HR_NRLINE = unlist(HR_NRLINE)
HR_maxL = unlist(HR_maxL)
HR_L = unlist(HR_L)
HR_ENTR = unlist(HR_ENTR)
HR_LAM = unlist(HR_LAM)
HR_TT = unlist(HR_TT)

study = unlist(study)
group = unlist(group)
trial = unlist(trial)
condition = unlist(condition)


#dfOptimSurg <- dfOptim[c(1:25), (5:10)]

dfRQASURGAT = data.frame(study, group, trial, condition,HR_RR, HR_DET, HR_NRLINE, HR_maxL, HR_L, HR_ENTR, HR_LAM, HR_TT, Resp_RR, Resp_DET, Resp_NRLINE, Resp_maxL, Resp_L, Resp_ENTR, Resp_LAM, Resp_TT)


dfRQASURGAT = mutate(dfRQASURGAT, pair = "Surrogate")

#Make empty columns, so i can rbind
dfRQASURGAT$Respembed = NA
dfRQASURGAT$Respdelay = NA
dfRQASURGAT$Respradius = NA

dfRQASURGAT$HRembed = NA
dfRQASURGAT$HRdelay = NA
dfRQASURGAT$HRradius = NA

#reorder
dfRQASURGAT <- dfRQASURGAT[c(1:4, 22:27, 5:21)]
ALLCRQA <- rbind(allCRQA, dfRQASURGAT)



allCRQA <- read.delim("CRQARealShuff.csv", header = T, sep = ",")

#bind surgat and other two together
#AllCRQA <- rbind(allCRQA, dfRQASURGAT)
#Save this, eeeeh!!
write.csv(dfRQASURGAT, file = "CRQASurg.csv", row.names = F)

write.csv(ALLCRQA, file = "AllCRQA.csv", row.names = F)
```

 - Test whether crqa shows a difference between real and surrogate pairs

```{r}

library(sjmisc)
library(sjPlot)
#Heart rate

RR <- lm(HR_RR ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(HR_RealSurg_RR)

HR_RealSurg_DET <- lm(HR_DET ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(HR_RealSurg_DET)

HR_RealSurg_NRLINE <- lm(HR_NRLINE ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(HR_RealSurg_NRLINE)

HR_RealSurg_maxL <- lm(HR_maxL ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(HR_RealSurg_maxL)

HR_RealSurg_L <- lm(HR_L ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(HR_RealSurg_L)

HR_RealSurg_ENTR <- lm(HR_ENTR ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(HR_RealSurg_ENTR)

HR_RealSurg_LAM <- lm(HR_LAM ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(HR_RealSurg_LAM)

HR_RealSurg_TT <- lm(HR_TT ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(HR_RealSurg_TT)

lm_HRTINGY1A<- sjt.lm(HR_RealSurg_RR, HR_RealSurg_DET, HR_RealSurg_NRLINE,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)



lm_HRTINGY2A<- sjt.lm(HR_RealSurg_maxL, HR_RealSurg_L, HR_RealSurg_ENTR,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)



lm_HRTINGY3A<- sjt.lm(HR_RealSurg_LAM, HR_RealSurg_TT,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)



Resp_RealSurg_RR <- lm(Resp_RR ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(Resp_RealSurg_RR)

Resp_RealSurg_DET <- lm(Resp_DET ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(Resp_RealSurg_DET)

Resp_RealSurg_NRLINE <- lm(Resp_NRLINE ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(Resp_RealSurg_NRLINE)

Resp_RealSurg_maxL <- lm(Resp_maxL ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(Resp_RealSurg_maxL)

Resp_RealSurg_L <- lm(Resp_L ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(Resp_RealSurg_L)

Resp_RealSurg_ENTR <- lm(Resp_ENTR ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(Resp_RealSurg_ENTR)

Resp_RealSurg_LAM <- lm(Resp_LAM ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(Resp_RealSurg_LAM)

Resp_RealSurg_TT <- lm(Resp_TT ~ pair, ALLCRQA[ALLCRQA$pair == "Surrogate"|ALLCRQA$pair == "Real",])
summary(Resp_RealSurg_TT)


lm_RESPTINGY1A<- sjt.lm(Resp_RealSurg_RR, Resp_RealSurg_DET, Resp_RealSurg_NRLINE,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)



lm_RESPTINGY2A<- sjt.lm(Resp_RealSurg_maxL,Resp_RealSurg_L, Resp_RealSurg_ENTR,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)


lm_RESPTINGY3A<- sjt.lm(Resp_RealSurg_LAM, Resp_RealSurg_TT,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)





```




### Testing effects of conditions
 - make a (probably underpowered) mixed model testing effects of the different conditions on heart rate and respiration coordination
 - N.B: would it make sense to include surrogate pairs? and if so how? what would that tell you?

```{r}
library(sjPlot) # table functions
library(sjmisc) # sample data

#HEART RATE MODELS
str(ALLCRQA)

HR_RRm12 <- lmer(HR_RR ~ 1+condition + (1|group), dfRQA, REML = FALSE)
summary(HR_RRm12)

#Not significant
#Selfpaced b = 0.1541, SE = 0.7807, t = -1.918 p > 0.05
#
#RESP MODELS


HR_RRm12 <- lmer(Resp_RR ~ 1+condition + (1|group), dfRQA, REML = FALSE)
summary(HR_RRm12)







HR_DETm2 <- lmer(HR_DET ~ condition + (1|group) + (1|pair), ALLCRQA[ALLCRQA$pair == "Real"|ALLCRQA$pair == "Surrogate",], REML = FALSE)
summary(HR_DETm2)

HR_NRLINEm3 <- lmer(HR_NRLINE ~ 1+ condition + (1|group) + (1|pair), ALLCRQA[ALLCRQA$pair == "Real"|ALLCRQA$pair == "Surrogate",], REML = FALSE)
summary(HR_NRLINEm3)

HR_maxLm4 <- lmer(HR_maxL ~ 1+condition + (1|group) + (1|pair), ALLCRQA[ALLCRQA$pair == "Real"|ALLCRQA$pair == "Surrogate",], REML = FALSE)
summary(HR_maxLm4)

HR_Lm5<- lmer(HR_L ~ 1+ condition + (1|group) + (1|pair), ALLCRQA[ALLCRQA$pair == "Real"|ALLCRQA$pair == "Surrogate",], REML = FALSE)
summary(HR_Lm5)

HR_ENTRm6 <- lmer(HR_ENTR ~ 1+ condition + (1|group) + (1|pair), ALLCRQA[ALLCRQA$pair == "Real"|ALLCRQA$pair == "Surrogate",], REML = FALSE)
summary(HR_ENTRm6)


HR_LAMm7 <- lmer(HR_LAM ~ 1+ condition + (1+study|condition), ALLCRQA[ALLCRQA$pair == "Real"|ALLCRQA$pair == "Surrogate",], REML = FALSE)
summary(HR_LAMm7)


HR_TTm8 <- lmer(HR_TT ~ 1+ condition + (1|group) + (1|pair), ALLCRQA[ALLCRQA$pair == "Real"|ALLCRQA$pair == "Surrogate",], REML = FALSE)
summary(HR_TTm8)


HRTINGY1<- sjt.lmer(HR_RRm1,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)



HRTINGY2<- sjt.lmer(HR_maxLm4, HR_Lm5, HR_ENTRm6,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)



HRTINGY3<- sjt.lmer(HR_LAMm7, HR_TTm8,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)





#RESPIRATION MODELS


Resp_RRm1 <- lmer(Resp_RR ~ pair + condition + (1+study|condition), allCRQA)
summary(Resp_RRm1)

Resp_DETm2 <- lmer(Resp_DET ~ pair + condition + (1+study|condition), allCRQA)
summary(Resp_DETm2)

Resp_NRLINEm3 <- lmer(Resp_NRLINE ~ pair + condition + (1+study|condition), allCRQA)
summary(Resp_NRLINEm3)

Resp_maxLm4 <- lmer(Resp_maxL ~ pair + condition + (1+study|condition), allCRQA)
summary(Resp_maxLm4)

Resp_Lm5<- lmer(Resp_L ~ pair + condition + (1+study|condition), allCRQA)
summary(Resp_Lm5)

Resp_ENTRm6 <- lmer(Resp_ENTR ~ pair + condition + (1+study|condition), allCRQA)
summary(Resp_ENTRm6)


Resp_LAMm7 <- lmer(Resp_LAM ~ pair + condition + (1+study|condition), allCRQA)
summary(Resp_LAMm7)


Resp_TTm8 <- lmer(Resp_TT ~ pair + condition + (1+study|condition), allCRQA)
summary(Resp_TTm8)



RESPTINGY1<- sjt.lmer(Resp_RRm1, Resp_DETm2, Resp_NRLINEm3,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)


RESPTINGY2<- sjt.lmer(Resp_maxLm4, Resp_Lm5, Resp_ENTRm6,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)

RESPTINGY3<- sjt.lmer(Resp_LAMm7, Resp_TTm8,  show.std = FALSE, show.aic = TRUE, show.r2 = FALSE, emph.p = TRUE,  digits.p = 3,show.se = TRUE,digits.se = 3,show.re.var = TRUE, show.icc = FALSE,
         show.dev = TRUE,  digits.est = 3, digits.summary = 3)



```



### Effects of respiration coordination on heart rate coordination
 - describe how you would test those.
 - Optional: run the models and report them